### 2020-02-15 Common/chapters/transfer_learning.tex
Julien and Johan: transfer learning overview (figure)

\section{Process overview}
\label{sec:process_overview}
The approach consists in five different steps.
First of all, similar datasets are collected and processed in the same way. These datasets need to share common features. For example, DWI images (MRI sequence) and CT scans share the same color scheme and look alike (the same kind of tissue is visible, etc.). On the contrary, mammographies are completely different in that they the tissue is less visible FIGURE.

@@

Fifth, the previous step is also applied to the target dataset. These final two trainings aim at keeping the interesting features from the other datasets while learning specializing the model in the target dataset again. Hopefully, the new weight initialization resulting from the transfer learning will allow to reach better metric values than before the transfer learning. Usually, the best model

@@

\begin{figure}[!h]
\centering
\includegraphics[width=1\textwidth, keepaspectratio=true]{./figures/tl_parallel_run.png}
\caption{Transfer learning - Parallelization}
\label{fig:tl_parallel_run}
\end{figure}

>>>>

\section{Process overview}
\label{sec:process_overview}
The approach consists in five different steps. Figure \ref{fig:tl_overview} gives a visual representation of the following explanations.\\
First of all, similar datasets are collected and processed in the same way. These datasets need to share common features. For example, DWI images (MRI sequence) and CT scans share the same color scheme and look alike (the same kind of tissue is visible, etc.). On the contrary, mammographies are completely different in that they the tissue is less visible FIGURE.

@@

Fifth, the previous step is also applied to the target dataset. These final two trainings aim at keeping the interesting features from the other datasets while learning specializing the model in the target dataset again. Hopefully, the new weight initialization resulting from the transfer learning will allow to reach better metric values than before the transfer learning.

\begin{figure}[!h]
\centering
\noindent
\makebox[\textwidth]{
\includegraphics[width=1.2\textwidth, keepaspectratio=true]{./figures/tl_overview.png}
}
\caption{Transfer learning - Overview}
\label{fig:tl_overview}
\end{figure}

@@

\begin{figure}[!h]
\centering
\noindent
\makebox[\textwidth]{
\includegraphics[width=1.3\textwidth, keepaspectratio=true]{./figures/tl_parallel_run.png}
}
\caption{Transfer learning - Parallelization}
\label{fig:tl_parallel_run}
\end{figure}
